Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-06 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Reviewer 2; Comment D3.

The straightforward combinations of the quantifier rules of {\ND} either with the modal rules of {\NDK} or with axiom K and the necessitation rule are suitable for a higher-order modal logic where constants and variables are \emph{rigid}. From the point of view of a \emph{possible world semantics}, rigidity means that their interpretation is independent of the world in which they are being interpreted. Rigidity is tacitly assumed by most works investigating the ontological argument, and is explicitly assumed here. Nevertheless, it should be noted that its adequacy for the ontological argument has already been contested \citep{fitting}. Another assumption made here is that the quantification domains are constant (i.e. independent of the possible worlds). Neither G\"odel's manuscript nor Scott's manuscript reveal whether they use constant or varying domains, and this is also the case for many variants (e.g. \citep{hajek}). Nevertheless, some authors of variants \citep[footnotes 11 and 14]{and90} of G\"odel's ontological argument do explicitly state a preference for varying domains. Our choice of assuming constant domains is motivated by simplicity.

>>>>

The straightforward combinations of the quantifier rules of {\ND} either with the modal rules of {\NDK} or with axiom K and the necessitation rule are suitable for a higher-order modal logic where constants and variables are \emph{rigid}. From the point of view of a \emph{possible world semantics}, rigidity means that their interpretation is independent of the world in which they are being interpreted. Rigidity is tacitly assumed by most works investigating the ontological argument, and is explicitly assumed here. Nevertheless, it should be noted that its adequacy for the ontological argument has already been contested \citep{fitting}. Another assumption made here is that the quantification domains are constant (i.e. independent of the possible worlds). Neither G\"odel's manuscript nor Scott's manuscript reveal whether they use constant or varying domains, and this is also the case for many variants (e.g. \citep{hajek}). Nevertheless, some authors of variants \citep[footnotes 11 and 14]{and90} of G\"odel's ontological argument do explicitly state a preference for varying domains. Our choice of constant domains is motivated by simplicity. As is well-known, varying domain quantifiers (also known as \emph{actualistic} quantifiers) can be simulated by constant domain quantifiers (also known as \emph{possibilistic} quantifiers) guarded by a primitive \emph{existence} predicate\footnote{Formally, $\forall^e x. F[x] \equiv \forall x. E(x) \imp F[x]$ and $\exists^e x. F[x] \equiv \exists x. E(x) \wedge F[x]$}; therefore, the formalization of ontological arguments with varying domain quantification would be feasible in the natural deduction calculus presented here as well.
